Empirical Analysis of the Role of Energy in Economic Growth

### 2013-01-22 EconGrowth.Rnw
Now using the lapply function to "loop" over various statistical analyses. I have implemented lapply for CD and CDq at this point. I still need to do CDx.

<<setup,include=FALSE>>=
require(knitr)
require(lattice)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=FALSE)
opts_chunk$set(
  tidy=FALSE,
  fig.width=4.5,
  fig.height=3.8,
  out.width=".45\\textwidth",
  out.height=".38\\textwidth",
  comment=NA)
@

<<Load Data>>=
#################################
# This function loads data given a country name.
#
# countryName = a string of the 2-digit code for the country for which data is to be loaded. 
#   The file name from which data will be loaded is assumed to be of the form 
#   "<countryName>Data.txt". The file is assumed to exist in a subfolder of this project called "data".
#
# returns a matrix with the data that has been loaded
##
loadData <- function(countryName){
  # Read the data file as a table with a header.  
  fileName <- paste("data/", countryName, "Data.txt", sep="")
  dataTable <- read.table(fileName, header = TRUE)
  # Identifies the header names associated with dataTable
  print(names(dataTable))
  return(dataTable)
}
@

@@

cobbDouglas <- function(countryName){

@@

  summaryCD <- summary(modelCD) # Gives the nls summary table.
  #print(summaryCD)
  ciCD <- confint(modelCD, level = 0.95); ciCD # Displays confidence intervals for the CD model.

  # Calculate beta and its confidence interval and report it.
  alpha <- as.numeric(coef(modelCD)["alpha"])
  beta <- 1.0 - alpha
  beta.est <- deltaMethod(modelCD, "1 - alpha"); beta.est # Estimates beta and its standard error (SE).
  # Now calculate a confidence interval on beta
  dofCD <- summaryCD$df[2]; dofCD # Gives the degrees of freedom for the model.
  tvalCD <- qt(0.975, df = dofCD); tvalCD
  betaCICD <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCD * SE); betaCICD # Gives the confidence interval on beta.

@@

  # Combine all estimates and their confidence intervals into data frames with intelligent row names
  estCD <- data.frame(lambda = coef(modelCD)["lambda"], alpha = coef(modelCD)["alpha"], beta = beta, gamma = 0)
  #print(estCD)
  row.names(estCD) <- "Cobb-Douglas"
  #row.names(estCD) <- "Cobb-Douglas: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}$"
  # The [1] subscripts pick off the lower confidence interval
  lowerCD <- data.frame(lambda = ciCD["lambda","2.5%"], alpha = ciCD["alpha", "2.5%"], beta = betaCICD[1], gamma = NA) 
  row.names(lowerCD) <- "- 95% CI"
  # The [2] subscripts pick off the lower confidence interval
  upperCD <- data.frame(lambda = ciCD["lambda","97.5%"], alpha = ciCD["alpha", "97.5%"], beta = betaCICD[2], gamma = NA)
  row.names(upperCD) <- "+ 95% CI"

  # Now create the data for a table.
  dataCD <- rbind(upperCD, estCD, lowerCD)
  #print(dataCD)
  colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
  tableCD <- xtable(dataCD, caption=paste(countryName, " Cobb-Douglas, 1980-2011", sep=""), digit = c(4, 4, 2, 2, 1))
  #print(tableCD)
  return(tableCD)
}

tableCD <- cobbDouglas("US")
print(tableCD)

countries <- c("US", "CN")
tablesCD <- lapply(countries, cobbDouglas)
#tablesCD <- sapply(countries, cobbDouglas, USE.NAMES = TRUE)
@

<<CD Results, results='asis'>>=
print(tableCD, caption.placement="top")
# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
# line is not working at the present time. --MKH, 18 Jan 2012.
# print(tableCD, caption.placement="top", sanitize.text.function = function(x){x})
@

@@

<<cobbDouglasEnergy function>>=
###############################
# This function fits the Cobb Douglas production function including energy to historical data
# The functional form is
#
# iGDP = exp(lambda * itime) * iCapStk^alpha * iLabor^beta * iEnergy^gamma
# 
# iYear: time indexed to 0.0 at the first year [years since beginning of data set]
# iGDP = time series GDP data indexed to 1.0 at the first year [-]
# iCapStk = time series capital stock data indexed to 1.0 at the first year [-]
# iLabor = time series labor data indexed to 1.0 at the first year [-]
# iEnergy = time series energy data indexed to 1.0 at the first year [-]. 
#      This may be any of heat (iQ), exergy (iX), or useful work (iU).
# 
# returns a data object containing three rows and 5 columns.
#   col 1: lambda
#   col 2: alpha
#   col 3: beta
#   col 4: gamma
#   row 1: -95% CI for each parameter
#   row 2: estimate for each parameter
#   row 3: +95% CI for each parameter
#
# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
# energyColumnName is the name of the column to be used for energy.
#   This may be any of heat ("iQ"), exergy ("iX"), or useful work ("iU").
# energyString is the string to be used in table captions reprsenting the type of energy. Typically, "q", "x", or "u"
##
cobbDouglasEnergy <- function(countryName, energyColumnName, energyString){

@@

  # Reparameterize to ensure that we meet the constraints:
  # * alpha + beta + gamma = 1.0.
  # * alpha, beta, and gamma are all between 0.0 and 1.0.
  # To do this, we reparameterize as
  # * 0 < a < 1
  # * 0 < b < 1
  # * alpha = min(a, b)
  # * beta = b - a
  # * gamma = 1 - max(a, b)
  iEnergy <- dataTable[energyColumnName] #grabs the desired energy column
  lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
  alphaGuess <- 0.3 # a typical value for alpha
  betaGuess <- 0.7 # a typical value for beta
  modelCDe <- nls(iGDP ~ exp(lambda*iYear) * 
                    iCapStk^min(a,b) * iLabor^abs(b-a) * 
                    iEnergy^(1.0 - max(a,b)), 
                  algorithm = "port",
                  start = list(lambda=lambdaGuess, a=alphaGuess, b=alphaGuess+betaGuess),
                  lower = list(lambda=-Inf, a=0, b=0),
                  upper = list(lambda=Inf, a=1, b=1),
                  data = dataTable)
  aicCDe <- AIC(modelCDe, k=2) # Checks validity of the model. AIC stands for Akaike's Information Criterion
  print(aicCDe)

  summaryCDe <- summary(modelCDe) # Gives the nls summary table
  print(summaryCDe)

  # Provides confidence intervals on lambda, a, and b. But, we need CIs on alpha and beta.
  ciCDe <- confint(modelCDe, level = 0.95)
  print(ciCDe)

@@

  # Now calculate confidence intervals.
  dofCDe <- summaryCDe$df[2] # Gives the degrees of freedom for the model.
  print(dofCDe)
  tvalCDe <- qt(0.975, df = dofCDe)
  print(tvalCDe)
  betaCICDe <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCDe * SE) # Gives the confidence interval on beta.
  print(betaCICDe)
  gammaCICDe <- with(gamma.est, Estimate + c(-1.0, 1.0) * tvalCDe * SE) # Gives the confidence interval on alpha.
  print(gammaCICDe)

  # Combine all estimates and their confidence intervals into data frames with intelligent row names
  estCDe <- data.frame(lambda = lambda, alpha = alpha, beta = beta, gamma = gamma)
  print(estCDe);
  #row.names(estCDe) <- "Cobb-Douglas with e: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}e^{\\gamma}$"
  row.names(estCDe) <- paste("C-D with ", energyString, sep="")
  # The [1] subscripts pick off the lower confidence interval
  lowerCDe <- data.frame(lambda = ciCDe["lambda","2.5%"], alpha = ciCDe["a", "2.5%"], beta = betaCICDe[1], gamma = gammaCICDe[1])
  row.names(lowerCDe) <- "- 95% CI"
  # The [2] subscripts pick off the lower confidence interval
  upperCDe <- data.frame(lambda = ciCDe["lambda","97.5%"], alpha = ciCDe["a", "97.5%"], beta = betaCICDe[2], gamma = gammaCICDe[2])
  row.names(upperCDe) <- "+ 95% CI"

  # Now create the data for a table.
  dataCDe <- rbind(upperCDe, estCDe, lowerCDe)
  print(dataCDe)

  return(dataCDe)
}
@

@@

<<cdq>>=
countryName <- "US"
energyColumn <- "iQ"; energyString <- "q"
dataCDq <- cobbDouglasEnergy(countryName, energyColumn, energyString)
# TODO Develop a better caption for the table based on the data automatically.
tableCDq <- xtable(dataCDq, caption=paste(countryName, ", 1980-2011.", sep=""), digit = c(4, 4, 2, 2, 3))
#estCDe <- dataCDe[2]
#dataAll <- rbind(estCD, estCDe); dataAll
#tableAll <- xtable(dataAll, caption="U.S. 1980-2011, All Models.", digit = c(4, 4, 2, 2, 3))
@

<<CDq Results, results='asis'>>=

print(tableCDq, caption.placement="top")
# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
# line is not working at the present time. --MKH, 18 Jan 2012.
# print(tableCDe, sanitize.text.function = function(x){x})

@@

<<>>=
# Establish guess values for alpha, beta, and lambda.
phiGuess <- -20
betaGuess <- 0.5 # a typical value for beta (exponent on labor)
zetaGuess <- 0.0004 # a small value
lambda_LGuess <- 0.007 #assuming no technical progress on the labor-capital portion of the function
lambda_EGuess <- 0.008 #assuming no technical progress on the energy portion of the function

# Runs a non-linear least squares fit to the data with constraints
modelCESQ <- nls(iGDP ~ ((1-zeta) * (exp(lambda_L*iYear) * iLabor^beta * iCapStk^(1-beta))^phi 
                         + zeta*(exp(lambda_E*iYear) * iQ)^phi)^(1/phi), 
                 algorithm = "port",
                 control = nls.control(maxiter = 500, tol = 1e-06, minFactor = 1/1024, 
                                       printEval = FALSE, warnOnly = FALSE),
                 start = list(phi=phiGuess, beta=betaGuess, zeta=zetaGuess, lambda_L=lambda_LGuess, 
                              lambda_E=lambda_EGuess),
                 lower = list(phi=-Inf, beta=0, zeta=0, lambda_L=-Inf, lambda_E=-Inf),
                 upper = list(phi=0, beta=1, zeta=1, lambda_L=Inf, lambda_E=Inf),
                 data=dataTable)

# Gives the nls summary table
summary(modelCESQ)
xyplot( resid(modelCESQ) ~ fitted(modelCESQ) )
histogram( ~resid(modelCESQ) )
qqmath( ~resid(modelCESQ) )
@

>>>>

<<setup, include=FALSE>>=
require(knitr)
require(lattice)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=FALSE)
opts_chunk$set(
  tidy=FALSE,
  fig.width=4.5,
  fig.height=3.8,
  out.width=".45\\textwidth",
  out.height=".38\\textwidth",
  comment=NA)

# Statistical significance levels. We'll work with 95% CIs
ciLevel <- 0.95
ciHalfLevel <- ciLevel + (1.0-ciLevel)/2.0
# List of countries
countries <- c(US = "US", ZA = "ZA")
# List of energy types
energyTypes <- c(Q = "Q", X = "X", U = "U")
@

<<Load Data, include=FALSE>>=
#################################
# This function loads data given a country name.
#
# countryName = a string of the 2-digit code for the country for which data is to be loaded. 
#   The file name from which data will be loaded is assumed to be of the form 
#   "<countryName>Data.txt". The file is assumed to exist in a subfolder of this project called "data".
#
# returns a matrix with the data that has been loaded
##
loadData <- function(countryName){
  # Read the data file as a table with a header.  
  fileName <- paste("data/", countryName, "Data.txt", sep="")
  dataTable <- read.table(fileName, header = TRUE)
  # Identifies the header names associated with dataTable
  #print(names(dataTable))
  return(dataTable)
}
@

@@

#################################################
# Calculates parameter estimates and confidence intervals
# for the Cobb-Douglas production function given a country.
#
# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
#
# returns a vector of data for the Cobb-Douglas model. 
# First item is the +95% CI on all parameters
# Second item contains the parameter estimates
# Third item is the -95% CI on all parameters
# Each row has names: lambda, alpha, beta, gamma, corresponding to the parameters in the model.
##
cobbDouglasData <- function(countryName){

@@

  summaryCD <- summary(modelCD) # Gives the nls summary table.
  #print(summaryCD)
  ciCD <- confint(modelCD, level = ciLevel); ciCD # Displays confidence intervals for the CD model.

  # Calculate beta and its confidence interval and report it.
  alpha <- as.numeric(coef(modelCD)["alpha"])
  beta <- 1.0 - alpha
  beta.est <- deltaMethod(modelCD, "1 - alpha"); beta.est # Estimates beta and its standard error (SE).
  # Now calculate a confidence interval on beta
  dofCD <- summaryCD$df[2]; dofCD # Gives the degrees of freedom for the model.
  tvalCD <- qt(ciHalfLevel, df = dofCD); tvalCD
  betaCICD <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCD * SE); betaCICD # Gives the confidence interval on beta.

@@

  # Combine all estimates and their confidence intervals into data frames with intelligent row names
  estCD <- data.frame(lambda = coef(modelCD)["lambda"], alpha = coef(modelCD)["alpha"], beta = beta, gamma = 0)
  #print(estCD)
  row.names(estCD) <- "CD"
  #row.names(estCD) <- "Cobb-Douglas: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}$"
  # The [1] subscripts pick off the lower confidence interval
  lowerCD <- data.frame(lambda = ciCD["lambda","2.5%"], alpha = ciCD["alpha", "2.5%"], beta = betaCICD[1], gamma = NA) 
  row.names(lowerCD) <- "- 95% CI"
  # The [2] subscripts pick off the lower confidence interval
  upperCD <- data.frame(lambda = ciCD["lambda","97.5%"], alpha = ciCD["alpha", "97.5%"], beta = betaCICD[2], gamma = NA)
  row.names(upperCD) <- "+ 95% CI"

  # Now create the data for a table.
  dataCD <- rbind(upperCD, estCD, lowerCD)
  #print(dataCD)
  return(dataCD)
}

####################################
# Creates a LaTeX printable table from the data. This function first calls cobbDouglasData.
#
# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
#
# returns a printable LaTeX table from xtable.
##
cobbDouglasTable <- function(countryName){
  dataCD <- cobbDouglasData(countryName) 
  colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
  tableCD <- xtable(dataCD, caption=paste(countryName, " Cobb-Douglas, 1980-2011", sep=""), digit = c(4, 4, 2, 2, 1))
  #print(tableCD)
  return(tableCD)  
}
@

<<CD Analysis>>=
tablesCD <- lapply(countries, cobbDouglasTable)
@

<<CD Results, results='asis'>>=
print(tablesCD[["US"]], caption.placement="top")
print(tablesCD[["ZA"]], caption.placement="top")
# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
# line is not working at the present time. --MKH, 18 Jan 2012.
# print(tableCD, caption.placement="top", sanitize.text.function = function(x){x})
@

@@

<<cobbDouglasEnergy function>>=
###############################
# This function fits the Cobb Douglas production function including energy to historical data
# The functional form is
#
# iGDP = exp(lambda * itime) * iCapStk^alpha * iLabor^beta * iEnergy^gamma
# 
# iYear: time indexed to 0.0 at the first year [years since beginning of data set]
# iGDP = time series GDP data indexed to 1.0 at the first year [-]
# iCapStk = time series capital stock data indexed to 1.0 at the first year [-]
# iLabor = time series labor data indexed to 1.0 at the first year [-]
# iEnergy = time series energy data indexed to 1.0 at the first year [-]. 
#      This may be any of heat (iQ), exergy (iX), or useful work (iU).
# 
# returns a data object containing three rows and 5 columns.
#   col 1: lambda
#   col 2: alpha
#   col 3: beta
#   col 4: gamma
#   row 1: -95% CI for each parameter
#   row 2: estimate for each parameter
#   row 3: +95% CI for each parameter
#
# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
# energyColumnName is the name of the column to be used for energy.
#   This may be any of heat ("iQ"), exergy ("iX"), or useful work ("iU").
# energyString is the string to be used in table captions reprsenting the type of energy. Typically, "q", "x", or "u"
##
cobbDouglasEnergyData <- function(countryName, energyString){

  energyColumnName  <- paste("i", energyString, sep="")
  #print(energyColumnName)

@@

  # Reparameterize to ensure that we meet the constraints:
  # * alpha + beta + gamma = 1.0.
  # * alpha, beta, and gamma are all between 0.0 and 1.0.
  # To do this, we reparameterize as
  # * 0 < a < 1
  # * 0 < b < 1
  # * alpha = min(a, b)
  # * beta = b - a
  # * gamma = 1 - max(a, b)
  iEnergy <- dataTable[energyColumnName] #grabs the desired energy column
  lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
  alphaGuess <- 0.3 # a typical value for alpha
  betaGuess <- 0.7 # a typical value for beta
  modelCDe <- nls(iGDP ~ exp(lambda*iYear) * 
                    iCapStk^min(a,b) * iLabor^abs(b-a) * 
                    iEnergy^(1.0 - max(a,b)), 
                  algorithm = "port",
                  start = list(lambda=lambdaGuess, a=alphaGuess, b=alphaGuess+betaGuess),
                  lower = list(lambda=-Inf, a=0, b=0),
                  upper = list(lambda=Inf, a=1, b=1),
                  data = dataTable)
  aicCDe <- AIC(modelCDe, k=2) # Checks validity of the model. AIC stands for Akaike's Information Criterion
  #print(aicCDe)

  summaryCDe <- summary(modelCDe) # Gives the nls summary table
  #print(summaryCDe)

  # Provides confidence intervals on lambda, a, and b. But, we need CIs on alpha and beta.
  ciCDe <- confint(modelCDe, level = ciLevel)
  #print(ciCDe)

@@

  # Now calculate confidence intervals.
  dofCDe <- summaryCDe$df[2] # Gives the degrees of freedom for the model.
  #print(dofCDe)
  tvalCDe <- qt(ciHalfLevel, df = dofCDe)
  #print(tvalCDe)
  betaCICDe <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCDe * SE) # Gives the confidence interval on beta.
  #print(betaCICDe)
  gammaCICDe <- with(gamma.est, Estimate + c(-1.0, 1.0) * tvalCDe * SE) # Gives the confidence interval on alpha.
  #print(gammaCICDe)

  # Combine all estimates and their confidence intervals into data frames with intelligent row names
  estCDe <- data.frame(lambda = lambda, alpha = alpha, beta = beta, gamma = gamma)
  #print(estCDe);
  #row.names(estCDe) <- "Cobb-Douglas with e: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}e^{\\gamma}$"
  row.names(estCDe) <- paste("C-D with ", energyString, sep="")
  # The [1] subscripts pick off the lower confidence interval
  lowerCDe <- data.frame(lambda = ciCDe["lambda","2.5%"], alpha = ciCDe["a", "2.5%"], beta = betaCICDe[1], gamma = gammaCICDe[1])
  row.names(lowerCDe) <- "- 95% CI"
  # The [2] subscripts pick off the lower confidence interval
  upperCDe <- data.frame(lambda = ciCDe["lambda","97.5%"], alpha = ciCDe["a", "97.5%"], beta = betaCICDe[2], gamma = gammaCICDe[2])
  row.names(upperCDe) <- "+ 95% CI"

  # Now create the data for a table.
  dataCDe <- rbind(upperCDe, estCDe, lowerCDe)
  #print(dataCDe)
  return(dataCDe)
}

cobbDouglasEnergyTable <- function(countryName, energyType){
  dataCDe <- cobbDouglasEnergyData(countryName, energyType)
  tableCDe <- xtable(dataCDe, caption=paste(countryName, ", 1980-2011.", sep=""), digit = c(4, 4, 2, 2, 3))
  return(tableCDe)
}

@

@@

<<CDe analysis>>=
# Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
CDqTables <- lapply(countries, cobbDouglasEnergyTable, energyType="Q")
@

<<CDq Results, results='asis'>>=
print(CDqTables[["US"]], caption.placement="top")
print(CDqTables[["ZA"]], caption.placement="top")
# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
# line is not working at the present time. --MKH, 18 Jan 2012.
# print(tableCDe, sanitize.text.function = function(x){x})

@@

<<CES function>>=

ces <- function(countryName, energyColumnName, energyString){

  # Establish guess values for phi beta, zeta, lambda_L and lambda_E.
  phiGuess <- -20
  betaGuess <- 0.5 # a typical value for beta (exponent on labor)
  zetaGuess <- 0.0004 # a small value
  lambda_LGuess <- 0.007 #assuming no technical progress on the labor-capital portion of the function
  lambda_EGuess <- 0.008 #assuming no technical progress on the energy portion of the function

  # Runs a non-linear least squares fit to the data with constraints
  modelCES <- nls(iGDP ~ ((1-zeta) * (exp(lambda_L*iYear) * iCapStk^(1-beta) * iLabor^beta)^phi 
                           + zeta*(exp(lambda_E*iYear) * iQ)^phi)^(1/phi), 
                   algorithm = "port",
                   control = nls.control(maxiter = 500, tol = 1e-06, minFactor = 1/1024, 
                                         printEval = FALSE, warnOnly = FALSE),
                   start = list(phi=phiGuess, beta=betaGuess, zeta=zetaGuess, lambda_L=lambda_LGuess, 
                                lambda_E=lambda_EGuess),
                   lower = list(phi=-Inf, beta=0, zeta=0, lambda_L=-Inf, lambda_E=-Inf),
                   upper = list(phi=0, beta=1, zeta=1, lambda_L=Inf, lambda_E=Inf),
                   data=dataTable)

  aicCES <- AIC(modelCES, k=2) # Checks validity of the model. AIC stands for Akaike's Information Criterion
  print(aicCES)

  # Gives the nls summary table
  summaryCES <- summary(modelCES) # Gives the nls summary table
  print(summaryCES)

  # Provides confidence intervals on phi, beta, zeta, lambda_L, and lambda_E. But, we need the CI on alpha.
  ciCES <- confint(modelCES, level = ciLevel)
  print(ciCES)

  # Get the estimate for alpha
  beta <- as.numeric(coef(modelCES)["beta"])
  alpha <- 1.0 - beta
  alpha.est <- deltaMethod(modelCES, "1 - beta") # Estimates alpha and its standard error (SE).
  print(alpha.est)

  # Now calculate a confidence interval on alpha
  dofCES <- summaryCES$df[2]
  print(dofCES) # Gives the degrees of freedom for the model.
  tvalCES <- qt(ciHalfLevel, df = dofCES); tvalCES
  # Get confidence intervals for each parameter in the model
  alphaCICES <- with(alpha.est, Estimate + c(-1.0, 1.0) * tvalCES * SE) # CI on alpha.
  print(alphaCICES)

  # Assemble the data into data frames for the table.
  estCES <- data.frame(phi = coef(modelCES)["phi"], alpha = alpha, 
                       beta = coef(modelCES)["beta"], zeta = coef(modelCES)["zeta"], 
                       lambda_L = coef(modelCES)["lambda_L"], lambda_E = coef(modelCES)["lambda_E"])
  row.names(estCES) <- paste("CES with ", energyString, sep="")
  #print(estCES)  
  # The [1] subscripts pick off the lower confidence interval
  lowerCES <- data.frame(phi = ciCES["phi","2.5%"], alpha = alphaCICES[1], 
                         beta = ciCES["beta", "2.5%"], zeta = ciCES["zeta", "2.5%"],
                         lambda_L = ciCES["lambda_L", "2.5%"], lambda_E = ciCES["lambda_E", "2.5%"])
  row.names(lowerCES) <- "- 95% CI"
  # The [2] subscripts pick off the lower confidence interval
  upperCES <- data.frame(phi = ciCES["phi","97.5%"], alpha = alphaCICES[2], 
                         beta = ciCES["beta", "97.5%"], zeta = ciCES["zeta", "97.5%"],
                         lambda_L = ciCES["lambda_L", "97.5%"], lambda_E = ciCES["lambda_E", "97.5%"])
  row.names(upperCES) <- "+ 95% CI"

  # Now create the data for a table.
  dataCES <- rbind(upperCES, estCES, lowerCES)
  print(dataCES)
  return(dataCES)

  #xyplot( resid(modelCESQ) ~ fitted(modelCESQ) )
  #histogram( ~resid(modelCESQ) )
  #qqmath( ~resid(modelCESQ) )
}
@

<<CES with Q>>=
countryName <- "US"
energyColumn <- "iQ"; energyString <- "q"
dataCESq <- ces(countryName, energyColumn, energyString)
tableCESq <- xtable(dataCESq, caption=paste(countryName, ", 1980-2011.", sep=""), digit = c(4, 1, 2, 2, 6, 5, 5))
@

<<CESq Results, results='asis'>>=
print(tableCESq, caption.placement="top")
@
